Relationships in the extremes and their influence on competition and coexistence

### 2021-10-08 paper/Paper.Rnw
discussion

%Need something like the following, maybe
%Previously, storage effects were described as the contribution of covariance between the environment and competition to coexistence \citep{Chesson_2012, Ellner_2016, Ellner_2019}. 
%However, the description of storage effects as the covariance between drivers is a (potentially dangerous) misnomer in terminology, and we argue that storage effects, instead, should be described as the contribution of the relationship between drivers. 
%All aspects and contributing values of the relationship between environmental response and competitive pressure are not fully captured by only the covariance between them because a measure of covariance does not capture the strucutre of associativity throuhgout the distribution of the relationship and any asymmetries there may be. 
%Thus, aligning with the decomposition presented in \cite{Ellner_2019}, we propose storage effect can be broken down further into the contribution of ATA [to storage effect/coexistence] and the contribution of symmetric association [to storage effect/coexistence].

%I think ata specialists are a thing - if their competitor is ubiquitous, they can only live in places on the landscape 
%where there are atas. Could have a discussion para on it, if it does not make the results. Or both. BTW, ATA exclusion has a 
%similar thing going on - a species excluded by ATAs (and competition) can only live on the portions of the landscape where
%there are no ATAs. Could also describe the temporal way of it - the ATA specialist can only survive in a era/epoch for which there
%are ATAs in its local, otherwise it'll have to go dormant or move elsewhere.

@@

%Higher sigma means a more fluctuating and variable environment. Then, if environmental fluctuations become more variable, the effect of ATAs becomes more important and non-negligible (rescue or exclusion). 
%Delta=1 means no overlapping generations -  breaking the storage effect requirement of buffered population growth.

>>>>

Outline

\underline{Paragraph summarizing results of G1 and how it compares and builds on prior theory.} 
We provided a farther tertiary decomposition to MCT, 
extending the framework put forward by \citep{Ellner_2019}. 
We decompose the storage effect into two new terms, 
$\Delta_i^{[EC]}$, the contribution of ATAs, and $\Delta_i^{[E \nat C]}$, the contribution of correlation \emph{per se}. 
Previously, storage effects were described as the contribution
of covariance between the environment and competition to coexistence \citep{Chesson_2012, Ellner_2016, Ellner_2019}. 
However, the description of storage effects as the covariance between drivers
is a misnomer in terminology, and we propose that storage effects, instead, 
should be described as the contribution of the relationship between drivers. 
All aspects and of the relationship between environmental response and competitive pressure are not fully captured by only the covariance between them because a measure of covariance does not capture the structure of associativity throughout the distribution of the relationship and any asymmetries there may be. 
Thus, it is misleading to describe the contribution of the whole EC relationship 
as the contribution of EC covariance.
In addressing this inconsistency, we have separated the mechanisms of storage effect into the contribution of ATA [to storage effect/coexistence] and the contribution of correlation \emph{per se} [to storage effect/coexistence].

\underline{paragraph summarizing results of G2 and how it compares and builds on prior theory}
Furthermore, we have shown not only that is it possible to decompose storage effect into the effect of correlation \emph{per se} and the effect of ATAs, but this new term that holds the contribution of not only the correlation but the structure of the correlation is a non-negligible term, in the lottery model. Our result adds coexistence to the list of ecological theory/phenomena that ATAs have been found to be important for \citep{Ghosh_2020_AER, Ghosh_2020_Eco, Ghosh_2020_ecolevol, Ghosh_2021}. 
%Higher sigma means a more fluctuating and variable environment. Then, if environmental fluctuations become more variable, the effect of ATAs becomes more important and non-negligible (rescue or exclusion). 
%Delta=1 means no overlapping generations -  breaking the storage effect requirement of buffered population growth.

\underline{paragraph summarizing results of G3 and how it compares and builds on prior theory}
Not only is the contribution of ATA non-neglible but in some cases the presence of absence of ATA can mediate the result of competition between species, i.e., coexistence or extirpation. 
Our investigation is a simple one; 
the ATA present is a perfect correlation is exactly one half of the relationship, 
but varying degrees of ATA may produce a similar result as well. 
%maybe the above sentence should go in caveats/assumptions paragraph 
ATA specialist? Does this go in this paragraph
%I think ata specialists are a thing - if their competitor is ubiquitous, they can only live in places on the landscape 
%where there are atas. Could have a discussion para on it, if it does not make the results. Or both. BTW, ATA exclusion has a 
%similar thing going on - a species excluded by ATAs (and competition) can only live on the portions of the landscape where
%there are no ATAs. Could also describe the temporal way of it - the ATA specialist can only survive in a era/epoch for which there
%are ATAs in its local, otherwise it'll have to go dormant or move elsewhere.

\underline{paragraph summarizing results of G4 and how it compares and builds on prior theory}

\underline{how results apply to or inform patterns or management questions in real life}
ATA specialists?
climate change and ATA

\underline{caveats/assumptions that could change result}

\underline{conclude: how ur work answers/informs the broad question from the intro and lay out 2-3 key priorities for next research on this question}
We provided another showcase of the importance of ATAs in ecology, 
building on previous studies.
ATAs clearly have implications for coexistence and competition;
though more research is needed in exploring more complex models 
including spatiotemporal and multispecies models.
Hope to see this tertiary decomposition of MCT be applied to empirical research.
More investigations should be done to explore implications of ATAs 
to other ecological theories.

@@
